# Importing our dataset
```{r,echo=TRUE}
sales<-read.csv("http://bit.ly/CarreFourSalesDataset")
head(sales)
```

# Checking the data
```{r,echo=TRUE}
str(sales)
```
```{r,echo=TRUE}
summary(sales)
```
*Checking the number of rows and in our dataset*
```{r,echo=TRUE}
cat("Rows in dataset:", nrow(sales), "\nCols in dataset:", ncol(sales))
cat("\nThe dimension of the dataset is:", dim(sales))
```
#Perform Data Cleaning
*checking for duplicates*
```{r,echo=TRUE}
sum(duplicated(sales))
```
We don't have duplicated data.

*Checking for missing values*
```{r,echo=TRUE}
cat("\n the columns with missing data are:",colSums(is.na(sales)))
```
We also don't have missing data.

*Checking for outliers*
```{r,echo=TRUE}
boxplot(sales$Sales)
```
We have outliers in the sales column which will not drop.

# Anomaly Detection
** Installing anomalize package**
```{r}
install.packages("anomalize")
```
library(tidyverse)
library(anomalize)

**# Collect our time series data**
tidyverse_cran_downloads

# Detecting our anomalies
```{r,echo=TRUE}
tidyverse_cran_downloads %>%
    time_decompose(count) %>%
    anomalize(remainder) %>%
    time_recompose() %>%
    plot_anomalies(time_recomposed = TRUE, ncol = 3, alpha_dots = 0.5)
```
The anomalies are the points in red. They therefore need to be investigated.
