# Importing the dataset
```{r,echo=TRUE}
Carrefour<-read.csv("http://bit.ly/CarreFourDataset")
head(Carrefour)
```

# Filter Methods
** Installing and loading our caret package**
```{R,ECHO=true}
suppressWarnings(
        suppressMessages(if
                         (!require(caret, quietly=TRUE))
                install.packages("caret")))
library(caret)
```

** Installing and loading the corrplot package for plotting**
```{r,echo=TRUE}
suppressWarnings(
        suppressMessages(if
                         (!require(corrplot, quietly=TRUE))
                install.packages("corrplot")))
library(corrplot)
```

**Selecting the numerical data and excluding the categorical
```{r,echo=TRUE}
df<-Carrefour[,c(6,7,8,12,13,14,15,16)]
head(df)
```

```{r,echo=TRUE}
summary(df)
```

** Removing variables with zero variance**
```{r,echo=TRUE}
df_f<-df[,apply(df,2,var,na.rm=TRUE)!=0]
df_f
```

** Calculating the correlation matrix**
```{r,echo=TRUE}
correlationMatrix <- cor(df_f)
```

**Find attributes that are highly correlated**
```{r,echo=TRUE}
highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.75)
```

**Highly correlated attributes**
```{r,echo=TRUE}
highlyCorrelated

names(df_f[,highlyCorrelated])
```

** Removing Redundant Features** 
```{r,echo=TRUE} 
df_f2<-df_f[-highlyCorrelated]
```

# Performing our graphical comparison
```{r,echo=TRUE} 
par(mfrow = c(1, 2))
corrplot(correlationMatrix, order = "hclust")
corrplot(cor(df_f2), order = "hclust")
```
This represents the graphical correlation of the variables after removing the highly correlated variables.

# Wrapper Method
** Installing and loading our clustvarsel package**
suppressWarnings(
        suppressMessages(if
                         (!require(clustvarsel, quietly=TRUE))
                install.packages("clustvarsel")))
                         
library(clustvarsel)

**Installing and loading our mclust package**
suppressWarnings(
        suppressMessages(if
                         (!require(mclust, quietly=TRUE))
                install.packages("mclust")))
library(mclust)

** Sequential forward greedy search (default)**
```{r,echo=TRUE}
out = clustvarsel(df_f,g=)
out
```

** building the clustering model**
```{r,echo=TRUE}
Subset1 = df_f[,out$subset]
mod = Mclust(Subset1)
summary(mod)
```


# Embedded Methods
** We install and load our wskm package**

suppressWarnings(
        suppressMessages(if
                         (!require(wskm, quietly=TRUE))
                install.packages("wskm")))
library(wskm)

set.seed(2)
model <- ewkm(df_f, 3, lambda=2, maxiter=1000)

** Loading and installing our cluster package**

suppressWarnings(
        suppressMessages(if
                         (!require(cluster, quietly=TRUE))
                install.packages("cluster")))
library("cluster")

## Plotting
** Cluster Plot against 1st 2 principal components**
```{r,echo=TRUE}
clusplot(df_f, model$cluster, color=TRUE, shade=TRUE,
         labels=8, lines=1,main='Cluster Analysis for Carrefour')
```
Weights are calculated for each variable and cluster. 
They are a measure of the relative importance of each variable 
with regards to the membership of the observations to that cluster.

# Feature Ranking
** We install and load the required packages**
 
suppressWarnings(
        suppressMessages(if
                         (!require(FSelector, quietly=TRUE))
                install.packages("FSelector")))
library(FSelector)

** using the correlation coefficient as a unit of valuation**
```{r,echo=TRUE}
Scores <- linear.correlation(medv~., df_f)
Scores
```

**Determining our cutoff**
```{r,echo=TRUE}
Subset <- cutoff.k(Scores, 5)
as.data.frame(Subset)
```

**Getting our cutoff as a percentage**
```{r,echo=TRUE}
Subset2 <-cutoff.k.percent(Scores, 0.4)
as.data.frame(Subset2)
```

**Using entropy based approach**
```{r,echo=TRUE}
Scores2 <- information.gain(medv~.,df_f)
```

** Choosing Variables by cutoffSubset <- cutoff.k(Scores2, 5)**
```{r,echo=TRUE}
Subset3 <- cutoff.k(Scores2, 5)
as.data.frame(Subset3)
```

```{r,echo=TRUE}
Subset3 <- cutoff.k(Scores2, 5)
as.data.frame(Subset3)
```

-Feature selection has helped us reduce the number of features in our dataset
by excluding the highly correlated variables(Filter methods) or by including them without any change as compared to dimensionality reduction.
